Methodology for Assessing the State of the Practice for Domain X

### 2021-10-20 StateOfPractice/Methodology/Methodology.tex
Updates to time estimates in Section 12

\begin{enumerate}
\item Identify the domain (X). (Section~\ref{SecIdentifyDomain})
\item Ask the Domain Expert to create a top ten list of software packages in the
  domain. (Section~\ref{SecDomainExpert})
\item Meet with the Domain Expert to brief them on the overall objective,
  research proposal, research questions, measurement template, and developer
  interviews. (Section~\ref{SecDomainExpert}) \label{StepMeeting}
\item Identify broad list of candidate software packages in the domain.
  (Section~\ref{SecIdentifyCandSoft})
\item Preliminary filter of software packages list.
  (Section~\ref{SecInitialFilter})
\item Review software list with Domain Expert. (Section~\ref{SecDomainExpert})
\item Domain Analysis. (Section~\ref{SecDomainAnalysis})
\item Ask Domain Expert to vet domain analysis.
  (Section~\ref{SecDomainExpert})
\item Gather source code and documentation for each prospective software
  package.
\item Collect repository based information. (Section~\ref{SecEmpiricalMeasures})
\item Measure using measurement template. (Section~\ref{SecMeasureTemplate})
\item Survey developers (Section~\ref{SecSurveyQuestions})
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP})
% \item Identify a short list of top software packages, typically four to six, for
%   deeper exploration according to the AHP rankings of the measurements.
\item Ask Domain Expert to vet AHP ranking. (Section~\ref{SecDomainExpert})
%\item Rank short list. (Section~\ref{SecRankShortList})
\item Answer research questions (from Section~\ref{SecResearchQuestions}) and
document answers.
\end{enumerate}

@@

The Measurement Template is found in
Appendix~\ref{SecGradingTemplate}.  This template is used to track measurements
and quality scores for all of the software packages in the domain. For each
software package, we fill out one column of the template. This process can take
between 2 to 5 hours for each package.  Project developers can be contacted for
help regarding installation, if necessary, but a cap of about 2 hours should be
imposed on the entire installation process, to keep the overall measurement time
feasible.

@@

    Initial 1 hour meeting with domain expert plus meeting prep & 10
    \addtocounter{totHours}{10} \\

    Identify candidate software & 10 \addtocounter{totHours}{10} \\

    Filter software list & 5 \addtocounter{totHours}{5} \\

    Domain analysis & 20 \addtocounter{totHours}{20} \\

    Interaction with domain expert(s) (initial meeting, review software list,
    vet domain analysis, vet AHP ranking) & 10 \addtocounter{totHours}{10} \\

    Collect raw data and fill-in measurement template & 30
    \addtocounter{totHours}{30} \\

@@

    Conduct interviews & 15 \addtocounter{totHours}{15} \\

@@

    Analyze data and answer research questions & 30 \addtocounter{totHours}{30}
    \\

>>>>

\begin{enumerate}
\item Identify the domain (X). (Section~\ref{SecIdentifyDomain})
\item Ask the Domain Expert to create a top ten list of software packages in the
  domain. (Section~\ref{SecDomainExpert})
\item Meet with the Domain Expert to brief them on the overall objective,
  research proposal, research questions, measurement template, and developer
  interviews. (Section~\ref{SecDomainExpert}) \label{StepMeeting}
\item Identify broad list of candidate software packages in the domain.
  (Section~\ref{SecIdentifyCandSoft})
\item Preliminary filter of software packages list.
  (Section~\ref{SecInitialFilter})
\item Review software list with Domain Expert. (Section~\ref{SecDomainExpert})
\item Domain Analysis (with the help of the Domain Expert).
(Section~\ref{SecDomainAnalysis})
\item Ask Domain Expert to vet domain analysis.
  (Section~\ref{SecDomainExpert})
\item Gather source code and documentation for each prospective software
  package.
\item Collect repository based information. (Section~\ref{SecEmpiricalMeasures})
\item Measure using measurement template. (Section~\ref{SecMeasureTemplate})
\item Survey developers (Section~\ref{SecSurveyQuestions})
\item Use AHP process to rank the software packages. (Section~\ref{SecAHP})
% \item Identify a short list of top software packages, typically four to six, for
%   deeper exploration according to the AHP rankings of the measurements.
\item Ask Domain Expert to vet AHP ranking. (Section~\ref{SecDomainExpert})
%\item Rank short list. (Section~\ref{SecRankShortList})
\item Answer research questions (from Section~\ref{SecResearchQuestions}) and
document answers.
\end{enumerate}

@@

The Measurement Template is found in Appendix~\ref{SecGradingTemplate}.  This
template is used to track measurements and quality scores for all of the
software packages in the domain. For each software package, we fill out one
column of the template. This process can take between 1 to 4 hours for each
package.  Project developers can be contacted for help regarding installation,
if necessary, but a cap of about 2 hours should be imposed on the entire
installation process, to keep the overall measurement time feasible.

@@

    Initial 1 hour meeting with domain expert plus meeting prep & 5
    \addtocounter{totHours}{5} \\

    Identify broad list of candidate software
    (Section~\ref{SecIdentifyCandSoft}) & 12 \addtocounter{totHours}{12} \\

    Filter software list (Section~\ref{SecInitialFilter}) (10 minutes per
    package for 30 packages) & 5 \addtocounter{totHours}{5} \\

	Review software list with Domain Expert (Section~\ref{SecDomainExpert}) & 2
	\addtocounter{totHours}{2} \\

    Domain analysis (with help of Domain Expert)
    (Section~\ref{SecDomainAnalysis}) & 25 \addtocounter{totHours}{20} \\

	Vet domain analysis with Domain Expert (Section~\ref{SecDomainExpert}) & 3
	\addtocounter{totHours}{3} \\

	Gather source code and documentation for each package (20 minutes per
	package for 30 packages)) & 10 \addtocounter{totHours}{10} \\

    Collect repository based data (Section~\ref{SecEmpiricalMeasures}) (10
    minutes per package for 30 packages) & 5 \addtocounter{totHours}{5} \\

	Measure using measurement template (Section~\ref{SecMeasureTemplate}) (2.5
    hours per repo for 30 repos) & 75 \addtocounter{totHours}{75} \\

@@

    Conduct interviews (1.5 hour interviews with 10 developers (assuming 1 in 3
    developers agree to an interview)) & 15 \addtocounter{totHours}{15} \\

@@

	Work with Domain Expert to vet AHP ranking & 2 \addtocounter{totHours}{2} \\

    Analyze data and answer research questions & 30 \addtocounter{totHours}{30}\\
